---
title: ""
output:
  word_document:
    reference_docx: ../templates/HSCA_briefing_monthly_AE_template.docx
---
::: {custom-style="Heading 1"}
Note on Quality Assessment
:::

::: {custom-style="Normal"}
This **Monthly A&E PRA HSCA briefing** is an automated report and requires some QA to ensure outputs have been produced properly. Steps include:

- Check all contact information (analysts and comms) are up to date, as these may have been temporary cover.
- Check the dates to ensure these have correctly updated.

**Please see the automated report below.**
:::

\newpage

::: {custom-style="Heading 1"}
Annex 1 [MONTHLY A&E WAITING TIMES STATISTICS (`r toupper(format(monthly_dates$date_this_month, "%B %Y"))`)](https://www.publichealthscotland.scot/data-and-intelligence/ae-activity/)
:::

::: {custom-style="Normal"}
**Lead Minister:** Cabinet Secretary for Health and Care

**Designation:** Accredited Official Statistics

**Target/commitment:** 95% 4-hour performance across all sites.

**Next update and frequency:** `r format(monthly_dates$date_next_update, "%d %B %Y")`; monthly

```{r results='asis', echo=FALSE}
if (nzchar(missing_boards_message)) {

  cat('::: {custom-style="WarningMessage"}\n\n')

  cat(missing_boards_message)

  cat('\n\n:::\n')

}
```

**Summary:** [WRITE SUMMARY HERE]

**Key points:**

```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics(
  here::here(
    "outputs",
    "monthly-4hr-performance-chart.png"
  )
)
```

- Monthly figures for `r format(monthly_dates$date_this_month, "%B %Y")` show that performance against the four-hour A&E target was:
  - `r monthly_values_all$perf4hr_this_month`% for All sites, `r up_down(monthly_values_all$perf4hr_diff_last_year)` compared to `r monthly_values_all$perf4hr_last_year`% in `r format(monthly_dates$date_last_year, "%B %Y")`.
  - `r monthly_values_type1$perf4hr_this_month`% for Core sites, `r up_down(monthly_values_type1$perf4hr_diff_last_year)` compared to `r monthly_values_type1$perf4hr_last_year`% in `r format(monthly_dates$date_last_year, "%B %Y")`.
  
- `r last_12_month_perf`

- The number of patients spending over 12 hours in A&E in `r format(monthly_dates$date_this_month, "%B %Y")` was `r comma(monthly_values_all$waits12hr_this_month)`, `r increase_decrease(monthly_values_all$waits12hr_diff_last_month)` of `r abs(monthly_values_all$waits12hr_diff_last_month)`% from last month and `r abs(monthly_values_all$waits12hr_diff_last_year)`% `r above_below(monthly_values_all$waits12hr_diff_last_year)` waits seen in `r format(monthly_dates$date_last_year, "%B")` last year.

- The number of attendances in A&E in `r format(monthly_dates$date_this_month, "%B %Y")` was `r comma(monthly_values_all$attendances_this_month)`, `r abs(monthly_values_all$attendances_diff_last_month)`% `r higher_lower(monthly_values_all$attendances_diff_last_month)` last month and `r abs(monthly_values_all$attendances_diff_last_year)`% `r above_below(monthly_values_all$attendances_diff_last_year)` attendances in `r format(monthly_dates$date_last_year, "%B")` last year.

- Five lowest performing boards this month (`r format(monthly_dates$date_this_month, "%B %Y")`) were: `r five_lowest_boards`.

- Five lowest performing sites this month (`r format(monthly_dates$date_this_month, "%B %Y")`) were: `r five_lowest_sites`.

- Scotland Core ED 4-hour performance in `r format(monthly_dates$date_this_month, "%B %Y")` was `r three_nations_values$perf4hr_scotland`%, this was `r abs(three_nations_values$perf4hr_diff_england)` percentage points `r higher_lower(three_nations_values$perf4hr_diff_england)` England Type 1 performance at `r three_nations_values$perf4hr_england`% and `r abs(three_nations_values$perf4hr_diff_wales)` percentage points `r higher_lower(three_nations_values$perf4hr_diff_wales)` Wales Major performance at `r three_nations_values$perf4hr_wales`%. 

**Note on data quality and limitations:** While the data undergo routine validation checks, differences in local service arrangements may affect comparisons between areas and over time. Due to the timeliness of data submissions and the dynamic nature of the A&E dataset, figures may be revised in subsequent publications.

Waiting times for Type 1 Departments in England and Major Departments in Wales are broadly comparable with Scottish Type 1 – Core sites. Other emergency care site types are not directly comparable across UK nations due to differences in definitions and service models.

**Contact information**

**Analysts**: Lucy Horner (Lucy.Horner@gov.scot); Katie Hendry (Katie.Hendry@gov.scot); Sophie Quinn (Sophie.Quinn2@gov.scot)

**Communications**: Laura Robertson (Laura.Robertson2@gov.scot); Ewan Smith (Ewan.Smith2@gov.scot); Jackie Stewart (Jackie.Stewart@gov.scot); Michael McHugh (Michael.McHugh@gov.scot) 
:::
